---
format: gfm
execute:
  warning: false
---

Please cite: 

> Judge-Lord, Devin and Karla Magana. 2024. A Dataset for Text Analysis of Project 2025. https://github.com/judgelord/2025


The raw Project 2025 body text (parsed by paragraph and cleaned up a bit): 

- [data/body_text_clean.rda](data/body_text_clean.rda)

```{r}
load(here::here("data", "body_text_clean.rda"))

body_text_clean$text[1:3]
```


A hand-coded crosswalk of the most relevant agency by section: 

- [data/agencies_by_section.csv](data/agencies_by_section.csv)
- [data/agencies_by_section.rda](data/agencies_by_section.rda)

```{r}
load(here::here("data", "agencies_by_section.rda"))

agencies_by_section
```

The Project 2025 body text, parsed by section, merged with the crosswalk, and department, agency, and other acronyms extracted from the text:

- [data/body_parsed.rda](data/body_parsed.rda)

```{r}
library(dplyr)

load(here::here("data", "body_parsed.rda"))

body_parsed[127,] |> mutate(across(everything(), as.character))
```


