---
title: "Project 2025"
format:
# pdf: default
 html:
   toc: true
   toc-location: left
  # theme: michigan.scss
execute:
  echo: false
  engine: knitr
  message: false
  warning: false
---

We parsed the Project 2025 "Mandate for Leadership" text by section and paragraph, linking each section to the federal department or agency it discussed. We also extracted acronyms from the text so that we can see which agencies are mentioned in the same paragraphs as other key terms. 

The parsed document and code for text analysis in R is here: <https://github.com/judgelord/2025>

Below are counts of key terms per section: 

# "Woke"

```{r}
#| echo: false
#| fig-height: 3

terms = c("woke")

source(here::here("code", "count_terms.R"))

d_department_plot
#d_agency_plot
d_subagency_name_plot
#d_subagency_acronym_plot
d_acronym_plot
```

# "Gender" 

```{r}
#| echo: false
#| fig-height: 4

terms = c("gender")

source(here::here("code", "count_terms.R"))

d_department_plot
# d_agency_plot
d_subagency_name_plot
# d_subagency_acronym_plot
d_acronym_plot
```

# Racialized language

```{r, echo=FALSE}
#| fig-height: 12
#| echo: false
#| 
racialized_terms <- read_csv(here::here("data", "racialized_terms.csv"))

terms <- racialized_terms$racialized_terms

terms

source(here::here("code", "count_terms.R"))

d_department_plot
#d_agency_plot
d_subagency_name_plot
```

```{r}
#| fig-height: 18
#| echo: false

#d_subagency_acronym_plot
d_acronym_plot
```
